Lasso_RCI_Response

### 2024-04-24 Lasso_RCI_Response.Rmd
seperate dfs and RCI with final analysis.

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")

@@

# 
# #devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_anx <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

DEP_JT <- JTRCIdf

@@

JT_DF<- ANX_JT

colnames(JT_DF) <- paste0(colnames(JT_DF),"_anx")

JT_DF2<- DEP_JT
colnames(JT_DF2) <- paste0(colnames(JT_DF2),"_dep")

JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
colnames(JT_DF)[1] = "ID1"

head(JT_DF)
```

@@

JT Numbers
```{r}
Mothership_post <- left_join(Mothership_post,JT_DF, by = join_by(ID1 == ID1)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    )),
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder)
    )
```

@@

AnxDep_PrePost <- data.frame(cbind(Mothership_post$ID1,
                                   Mothership_post$Disorder_treat,
                                   Mothership_post$BL_CUDOS,
                                   Mothership_post$BL_CUXOS,
                                   Mothership_post$CUDOS_pre,
                                   Mothership_post$CUDOS_post,
                                   Mothership_post$CUXOS_pre,
                                   Mothership_post$CUXOS_post,
                                   #Extra stuff?
                                   Mothership_post$Depression_Responder,
                                   Mothership_post$Anxiety_Responder
                                   #Mothership_post$RESPONDER_FIGS
)) #%>%
#filter(!is.na(Mothership_post$Disorder_treat))

colnames(AnxDep_PrePost) = c("ID1","Disorder_Type", "BL_CUDOS", "BL_CUXOS", "CUDOS_pre","CUDOS_post","CUXOS_pre","CUXOS_post","Depression_Responder",
                             "Anxiety_Responder")
#, "RESPONDER_FIGS")

#8. Create long data frame

AnxDep_PrePost_Long <- AnxDep_PrePost %>% 
  pivot_longer(
    cols = CUDOS_pre:CUXOS_post, 
    names_to = "Test",
    values_to = "Score"
  )
AnxDep_PrePost_Long <-AnxDep_PrePost_Long %>%
  mutate(
    PrePost = ifelse(
      Test == "CUDOS_pre", "Pre",
      ifelse(Test == "CUXOS_pre" , "Pre", "Post"
      )),
    Score = as.integer(Score),
    Test = as.factor(Test),
    Test = as.factor(ifelse(Test == "CUDOS_pre",  "CUDOS",
                            ifelse(Test == "CUDOS_post", "CUDOS", "CUXOS"
                            ))))

#9. Convert to data frame with means of values to be plotted
AnxDep_PrePost_mean<-AnxDep_PrePost_Long %>%
  group_by(Test,PrePost) %>%
  summarise(Score=mean(Score,na.rm=TRUE))
```

# Data analysis 
## Part 1: Who is attending?

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
Mothership_lasso <- Mothership_post |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Anxiety_Responder),
    !is.na(Depression_Responder),
    CUXOS_pre >= 20,
    CUDOS_pre >= 20
  ) |>
  select( c(
    Anxiety_Responder, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))

Mothership_lasso <- na.omit(Mothership_lasso)

library(tableone)

### first gather information based upon anxiety

## Vector of variables to summarize
table1_vars_anx <- c("Anxiety_Responder",colnames(Mothership_lasso)[-1:-3])
table1_vars_anx <- table1_vars_anx[1:28]

colnames(Mothership_lasso)[-1]
## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
```

```{r}
## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
table1_tab_anx <- data.frame(table1_tab_anx)
table1_tab_anx<- table1_tab_anx[-2,]

# add discriptive statistics 
table1_tab_anx$ef_size = c("")

@@

table1_tab_anx[2,4] <- round(t_test(Age_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[2,5] <- round(cohens_d(Age_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[3,4] <- round(chisq.test(Mothership_lasso$Some_College, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[3,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Some_College))$estimate,2)

@@

table1_tab_anx[4,4] <- round(chisq.test(Mothership_lasso$Female, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[4,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Female))$estimate,2)

@@

table1_tab_anx[5,4] <- round(chisq.test(Mothership_lasso$Married, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[5,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Married))$estimate,2)

@@

table1_tab_anx[6,4] <- round(chisq.test(Mothership_lasso$White, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[6,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$White))$estimate,2)

@@

table1_tab_anx[7,4] <- round(chisq.test(Mothership_lasso$IPT_track_1, Mothership_lasso$Anxiety_Responder)$statistic,2)
OR_IPT_anx <- table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$IPT_track_1)

@@

table1_tab_anx[9,5] <- round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$estimate,2)
table1_tab_anx[9,3] <-

@@

@@

table1_tab_anx[10,3] <-

@@

table1_tab_anx[11,4] <- round(t_test(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[11,5] <- round(cohens_d(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[12,4] <- round(t_test(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[12,5] <- round(cohens_d(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[13,4] <- round(chisq.test(Mothership_lasso$Anxiety_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[13,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Anxiety_D))$estimate,2)

@@

table1_tab_anx[14,4] <- round(chisq.test(Mothership_lasso$Mood_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[14,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Mood_D))$estimate,2)

@@

table1_tab_anx[15,4] <- round(chisq.test(Mothership_lasso$BPD_P, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[15,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$BPD_P))$estimate,2)

@@

table1_tab_anx[16,4] <- round(chisq.test(Mothership_lasso$Trauma_D, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[16,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Trauma_D))$estimate,2)

@@

table1_tab_anx[17,4] <- round(chisq.test(Mothership_lasso$Other, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[17,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Other))$estimate,2)

@@

table1_tab_anx[18,4] <- round(chisq.test(Mothership_lasso$Anxiety_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[18,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Anxiety_C))$estimate,2)

@@

table1_tab_anx[19,4] <- round(chisq.test(Mothership_lasso$Mood_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[19,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Mood_C))$estimate,2)

@@

table1_tab_anx[20,4] <- round(chisq.test(Mothership_lasso$BPD_Co_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[20,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$BPD_Co_C))$estimate,2)

@@

table1_tab_anx[21,4] <- round(chisq.test(Mothership_lasso$Trauma_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[21,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Trauma_C))$estimate,2)

@@

table1_tab_anx[22,4] <- round(chisq.test(Mothership_lasso$Substance_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[22,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Substance_C))$estimate,2)

@@

table1_tab_anx[23,4] <- round(chisq.test(Mothership_lasso$Other_C, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[23,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$Other_C))$estimate,2)

@@

table1_tab_anx[24,4] <- round(chisq.test(Mothership_lasso$No_Co, Mothership_lasso$Anxiety_Responder)$statistic,2)
table1_tab_anx[24,5] <- round(fisher.test(table(Mothership_lasso$Anxiety_Responder,Mothership_lasso$No_Co))$estimate,2)

@@

table1_tab_anx[25,4] <- round(t_test(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[25,5] <- round(cohens_d(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[26,4] <- round(t_test(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[26,5] <- round(cohens_d(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[27,4] <- round(t_test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[27,5] <- round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[28,4] <- round(t_test(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[28,5] <- round(cohens_d(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[29,4] <- round(t_test(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[29,5] <- round(cohens_d(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

table1_tab_anx[30,4] <- round(t_test(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso)$statistic,2)
table1_tab_anx[30,5] <- round(cohens_d(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso)$effsize,2)

@@

>>>>

## Read in the dataset. 
```{r}
Mothership <- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
#DF_1<- read_sav("~/Desktop/Coding/data/PHPoutcome_clean.sav")
dim(Mothership)
```

@@

# 
# #devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_anx <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

DEP_JT <- JTRCIdf
colnames(DEP_JT) <- paste0(colnames(DEP_JT),"_dep")
head(DEP_JT)

@@

# JT_DF<- ANX_JT

colnames(ANX_JT) <- paste0(colnames(ANX_JT),"_anx")

# 
# JT_DF2<- DEP_JT

# 
# JT_DF <- full_join(JT_DF,JT_DF2, by = c("ppid_anx" = "ppid_dep"))
# colnames(JT_DF)[1] = "ID1"

head(ANX_JT)
```

JTRCI with less people
```{r}

RCI_df_anx2 <- Mothership_post |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUXOS_pre),
    !is.na(CUXOS_post),
    CUXOS_pre > 20,
  )|>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- Mothership_post |>
  filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(CUDOS_pre),
    !is.na(CUDOS_post),
    CUDOS_pre > 20,
  ) |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUXOS_pre),
    post = as.numeric(CUXOS_post),
  ) |>
  select(
    ID1,pre,post
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

RCI_df_dep2 <- data.frame(RCI_df_dep2)
RCI_df_anx2 <- data.frame(RCI_df_anx2)

#1. JT classification for depression
JTRCI (data = RCI_df_dep2, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  JTcrit = "auto",
                  plottitle = "JT indices for Depression")

DEP_JT_smol <- JTRCIdf
colnames(DEP_JT_smol) <- paste0(colnames(DEP_JT_smol),"_dep")
head(DEP_JT_smol)

#2. JT classification for anxiety
JTRCI (data = RCI_df_anx2, 
                  pre = "pre", 
                  post = "post", 
                  ppid = "ID1", 
                  reliability = .74, 
                  indextype = "JT", 
                  #JTcrit = "auto",
                  plottitle = "JT Indices For Anxiety")

ANX_JT_smol<- JTRCIdf

colnames(ANX_JT_smol) <- paste0(colnames(ANX_JT_smol),"_anx")

head(ANX_JT_smol)

view(ANX_JT_smol)
```

@@

JT Numbers
```{r}
Mothership_post_anx <- left_join(Mothership_post,ANX_JT_smol, by = join_by(ID1 == ppid_anx)) |>
  mutate(
    Anxiety_Responder = ifelse(!is.na(class_JTRCI_anx), class_JTRCI_anx, NA),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "1" = "2",
                                         "2" = "2",
                                         "3" = "1",
                                         "4" = "1",
                                         "5" = "1"
    )),
    Anxiety_Responder = as.factor(ifelse(!is.na(Anxiety_Responder), Anxiety_Responder, Anx_Responder)),
    Anxiety_Responder = as.factor(recode(Anxiety_Responder,
                                         "2" = "Non-Responder",
                                         "1" = "Responder"
    ))) |>
  filter(
    !is.na(Anxiety_Responder),
    )

Mothership_post_dep <- left_join(Mothership_post,DEP_JT_smol, by = join_by(ID1 == ppid_dep)) |>
  mutate(
    Depression_Responder = ifelse(!is.na(class_JTRCI_dep), class_JTRCI_dep, NA),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "1" = "2",
                                            "2" = "2",
                                            "3" = "1",
                                            "4" = "1",
                                            "5" = "1"
    )),
    Depression_Responder = as.factor(ifelse(!is.na(Depression_Responder), Depression_Responder, Dep_Responder)),
    Depression_Responder = as.factor(recode(Depression_Responder,
                                            "2" = "Non-Responder",
                                            "1" = "Responder"
    ))) |>
  filter(
    !is.na(Depression_Responder)
    )

Mothership_post_joined <- full_join(Mothership_post_dep,Mothership_post_anx, by = join_by(ID1 == ID1), suffix = c(".x",".y")) |>
  select(-ends_with(".y"))

#It saves everything colname.x, so I'm going to remove the .x from everything
names.x <- colnames(Mothership_post_joined)[2:248]
colnames(Mothership_post_joined)[2:248] <- substr(names.x,1,nchar(names.x)-2)
```

@@

AnxDep_PrePost <- data.frame(cbind(Mothership_post_joined$ID1,
                                   Mothership_post_joined$Disorder_treat,
                                   Mothership_post_joined$BL_CUDOS,
                                   Mothership_post_joined$BL_CUXOS,
                                   Mothership_post_joined$CUDOS_pre,
                                   Mothership_post_joined$CUDOS_post,
                                   Mothership_post_joined$CUXOS_pre,
                                   Mothership_post_joined$CUXOS_post,
                                   #Extra stuff?
                                   Mothership_post_joined$Depression_Responder,
                                   Mothership_post_joined$Anxiety_Responder
                                   #Mothership_post$RESPONDER_FIGS
)) #%>%

# Data analysis 
## Part 1: Methods information
```{r}

## Part 2: Who is attending?

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown

First greate dfs for analyses

```{r}
### Anxeity 
Mothership_lasso_anx <- Mothership_post_anx |>
  filter(
  !is.na(Some_College),
  !is.na(Female),
  !is.na(IPT_track_1),
  !is.na(White),
  !is.na(Anxiety_Responder),
  CUXOS_pre >= 20,
  ) |>
  select( c(
    ID1,Anxiety_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))
Mothership_lasso_anx <- na.omit(Mothership_lasso_anx)

### depression
Mothership_lasso_dep <- Mothership_post_dep |>
    filter(
    !is.na(Some_College),
    !is.na(Female),
    !is.na(IPT_track_1),
    !is.na(White),
    !is.na(Depression_Responder),
    CUDOS_pre >= 20,
  ) |>
  select( c(
    ID1, Depression_Responder,Disorder_treat,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P, Trauma_D, Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs,
    #For table 3 - RCI info
    CUXOS_pre, CUXOS_post, Delta_Anx_DC, CUDOS_pre, CUDOS_post, Delta_Dep_DC
  ))
Mothership_lasso_dep <- na.omit(Mothership_lasso_dep)

### joined df
Mothership_lasso_joined <- full_join(Mothership_lasso_anx,Mothership_lasso_dep, by = join_by("ID1" == "ID1")) |> 
    select(-ends_with(".y"))

#It saves everything colname.x, so I'm going to remove the .x from everything
names.x <- colnames(Mothership_lasso_joined)[3:34]
colnames(Mothership_lasso_joined)[3:34] <- substr(names.x,1,nchar(names.x)-2)

#Delete ID1 from dfs
Mothership_lasso_anx <- Mothership_lasso_anx[,-1]
Mothership_lasso_dep <- Mothership_lasso_dep[,-1]
```

```{r}

library(tableone) # This can be used to grab Exporatory data analysis values

### first gather information based upon anxiety
## Vector of variables to summarize
table1_vars_anx <- c(colnames(Mothership_lasso_anx)[-1:-2])
table1_vars_anx <- table1_vars_anx[1:27]

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Other", 
             "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )

## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Mothership_lasso_anx,strata ="Anxiety_Responder",  factorVars = catVars, addOverall = T)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
table1_tab_anx <- data.frame(table1_tab_anx)
table1_tab_anx
# add discriptive statistics 
table1_tab_anx$ef_size = c("")

@@

table1_tab_anx[2,5] <- round(t_test(Age_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[2,6] <- round(cohens_d(Age_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[3,5] <- round(chisq.test(Mothership_lasso_anx$Some_College, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[3,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Some_College))$estimate,2)

@@

table1_tab_anx[4,5] <- round(chisq.test(Mothership_lasso_anx$Female, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[4,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Female))$estimate,2)

@@

table1_tab_anx[5,5] <- round(chisq.test(Mothership_lasso_anx$Married, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[5,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Married))$estimate,2)

@@

table1_tab_anx[6,5] <- round(chisq.test(Mothership_lasso_anx$White, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[6,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$White))$estimate,2)

@@

table1_tab_anx[7,5] <- round(chisq.test(Mothership_lasso_anx$IPT_track_1, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
OR_IPT_anx <- table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$IPT_track_1)

@@

table1_tab_anx[9,6] <- round(fisher.test(cbind(OR_IPT_anx[,"General"],OR_IPT_anx[,"Trauma"]))$estimate,2)
table1_tab_anx[9,5] <-

@@

table1_tab_anx[10,6] <- 

@@

@@

table1_tab_anx[11,5] <- round(t_test(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[11,6] <- round(cohens_d(Days_complete_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[12,5] <- round(t_test(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[12,6] <- round(cohens_d(Days_not_attended_1 ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[13,5] <- round(chisq.test(Mothership_lasso_anx$Anxiety_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[13,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Anxiety_D))$estimate,2)

@@

table1_tab_anx[14,5] <- round(chisq.test(Mothership_lasso_anx$Mood_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[14,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Mood_D))$estimate,2)

@@

table1_tab_anx[15,5] <- round(chisq.test(Mothership_lasso_anx$BPD_P, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[15,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$BPD_P))$estimate,2)

@@

table1_tab_anx[16,5] <- round(chisq.test(Mothership_lasso_anx$Trauma_D, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[16,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Trauma_D))$estimate,2)

@@

table1_tab_anx[17,5] <- round(chisq.test(Mothership_lasso_anx$Other, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[17,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Other))$estimate,2)

@@

table1_tab_anx[18,5] <- round(chisq.test(Mothership_lasso_anx$Anxiety_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[18,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Anxiety_C))$estimate,2)

@@

table1_tab_anx[19,5] <- round(chisq.test(Mothership_lasso_anx$Mood_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[19,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Mood_C))$estimate,2)

@@

table1_tab_anx[20,5] <- round(chisq.test(Mothership_lasso_anx$BPD_Co_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[20,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$BPD_Co_C))$estimate,2)

@@

table1_tab_anx[21,5] <- round(chisq.test(Mothership_lasso_anx$Trauma_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[21,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Trauma_C))$estimate,2)

@@

table1_tab_anx[22,5] <- round(chisq.test(Mothership_lasso_anx$Substance_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[22,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Substance_C))$estimate,2)

@@

table1_tab_anx[23,5] <- round(chisq.test(Mothership_lasso_anx$Other_C, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[23,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$Other_C))$estimate,2)

@@

table1_tab_anx[24,5] <- round(chisq.test(Mothership_lasso_anx$No_Co, Mothership_lasso_anx$Anxiety_Responder)$statistic,2)
table1_tab_anx[24,6] <- round(fisher.test(table(Mothership_lasso_anx$Anxiety_Responder,Mothership_lasso_anx$No_Co))$estimate,2)

@@

table1_tab_anx[25,5] <- round(t_test(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[25,6] <- round(cohens_d(Current_Dx ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[26,5] <- round(t_test(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[26,6] <- round(cohens_d(CUDOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[27,5] <- round(t_test(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[27,6] <- round(cohens_d(CUXOS_pre ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[28,5] <- round(t_test(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[28,6] <- round(cohens_d(rdqPOST_coping ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[29,5] <- round(t_test(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[29,6] <- round(cohens_d(rdqPOST_pmh ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_anx[30,5] <- round(t_test(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso_anx)$statistic,2)
table1_tab_anx[30,6] <- round(cohens_d(rdqPOST_func ~ Anxiety_Responder, data = Mothership_lasso_anx)$effsize,2)

@@

table1_tab_dep
